% Everything with --rus inside is supposed to be written in russian
\title{Computational modeling of magnetic materials}
\titlerus{Компьютерное моделирование магнитных материалов}

\author{Dmitry Volkov}
\authorrus{Дмитрий Волков}

\department{Materials Science}
\departmentrus{Материаловедение}

\degree{22.04.01 Materials Science and Engineering}
\degreerus{22.04.01 Материаловедение и технологии материалов}

\degreemonth{June}
\degreeyear{2021}
\thesisdate{June 18, 2021}
\degreemonthrus{Июнь}
\thesisdaterus{Июнь 18, 2021}

\supervisor{Artem R. Oganov}{Full Professor}{Habilitation, PhD}
\supervisorrus{Артём Ромаевич Оганов}{Профессор РАН}{д-р физ.-мат. наук}

\chairman{Arthur C. Smith}{Chairman, Department Committee on Graduate Theses}


\maketitle
\rusmaketitle

\setcounter{savepage}{\thepage}
\begin{abstractpage}
\input{chapters/abstract}
\end{abstractpage}

 \setcounter{page}{\thesavepage}
 \begin{abstractpagerus}
 \input{chapters/abstract_rus}
 \end{abstractpagerus}


\section*{\centering Acknowledgments}

I would like to express my gratitude to my research advisor, prof.  Artem R. Oganov for the kind support and guidance in this master thesis.

I want to extend my thanks to colleges from the laboratory Dr. Zahed Allahyari,  Dr. Christian Tantardini, and Michele Galasso,  who have readily helped me analyze difficult calculations and guide me through this complicated work.

I would like to express appreciation to prof.  Andriy Zhugaevich and Dr. Dmitry Aksyonov for the guidance, support, and useful hints on the very first steps of this project.

Also, I want to thank prof. Sergey Levchenko for the guidance and advisory on the part of the project related to machine learning algorithms as well as for the productive discussion. 
